Brownian Dynein Model

### 2016-05-11 latex/paper.tex
Add new test for +x forces, still needs work.

\[
\begin{pmatrix}
  -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
  & -\frac{X_{nm}-X_{nb}}{\gamma} & \frac{X_{t}-X_{nm}}{\gamma} & 0 & 0\\
  -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
  & 0 & -\frac{X_{t}-X_{nm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
  -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
  & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
  -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
  & -\frac{Y_{nm}-Y_{nb}}{\gamma} & \frac{Y_{t}-Y_{nm}}{\gamma} & 0 & 0\\
  -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
  & 0 & -\frac{Y_{t}-Y_{nm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
  -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}
  & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
\end{pmatrix}
\begin{pmatrix}
  \dot{L}_n\\
  \dot{L}_f\\
  \lambda_{ns}\\
  \lambda_{nt}\\
  \lambda_{ft}\\
  \lambda_{fs}\\
\end{pmatrix}
=
\begin{pmatrix}
  -\frac{F_{xml}}{\gamma} - R_{xml}\\
  -\frac{F_{xt}}{\gamma} - R_{xt}\\
  -\frac{F_{xmr}}{\gamma} - R_{xmr}\\
  -\frac{F_{yml}}{\gamma} - R_{yml}\\
  -\frac{F_{yt}}{\gamma} - R_{yt}\\
  -\frac{F_{ymr}}{\gamma} - R_{ymr}\\
\end{pmatrix}
\]

>>>>

\[
\begin{pmatrix}
  -\frac{X_{nm}}{Ln} & -\frac{X_{nm}}{Lf}
  & -\frac{X_{nm}-X_{nb}}{\gamma} & \frac{X_{t}-X_{nm}}{\gamma} & 0 & 0\\
  -\frac{X_{t}}{Ln} & -\frac{X_{t}}{Lf}
  & 0 & -\frac{X_{t}-X_{nm}}{\gamma} & \frac{X_{fm}-X_{t}}{\gamma} & 0\\
  -\frac{X_{fm}}{Ln} & -\frac{X_{fm}}{Lf}
  & 0 & 0 & -\frac{X_{fm}-X_{t}}{\gamma} & \frac{X_{fb}-X_{fm}}{\gamma}\\
  -\frac{Y_{nm}}{Ln} & -\frac{Y_{nm}}{Lf}
  & -\frac{Y_{nm}-Y_{nb}}{\gamma} & \frac{Y_{t}-Y_{nm}}{\gamma} & 0 & 0\\
  -\frac{Y_{t}}{Ln} & -\frac{Y_{t}}{Lf}
  & 0 & -\frac{Y_{t}-Y_{nm}}{\gamma} & \frac{Y_{fm}-Y_{t}}{\gamma} & 0\\
  -\frac{Y_{fm}}{Ln} & -\frac{Y_{fm}}{Lf}
  & 0 & 0 & -\frac{Y_{fm}-Y_{t}}{\gamma} & \frac{Y_{fb}-Y_{fm}}{\gamma}\\
\end{pmatrix}
\begin{pmatrix}
  \dot{L}_n\\
  \dot{L}_f\\
  \lambda_{ns}\\
  \lambda_{nt}\\
  \lambda_{ft}\\
  \lambda_{fs}\\
\end{pmatrix}
=
\begin{pmatrix}
  -\frac{F_{nmx}}{\gamma} - R_{nmx}\\
  -\frac{F_{tx}}{\gamma} - R_{tx}\\
  -\frac{F_{fmx}}{\gamma} - R_{fmx}\\
  -\frac{F_{nmy}}{\gamma} - R_{nmy}\\
  -\frac{F_{ty}}{\gamma} - R_{ty}\\
  -\frac{F_{fmy}}{\gamma} - R_{fmy}\\
\end{pmatrix}
\]
